\hypertarget{index_intro_sec}{}\section{Introduction}\label{index_intro_sec}
The S\+K\+IZ operator algorithm, described by Sequeira and Preteux in \mbox{[}1\mbox{]}, is an efficient way of calculating and maintaining a Voronoi diagram in discrete 2D space. Unlike other, more popular algorithms such as Fortune\textquotesingle{}s Sweep, the S\+K\+IZ algorithm is dynamic so adding and removing seeds does not require recalculation of the entire graph. Moreover, checking the bounds of a region R(s) and checking whether a pixel p belongs to a region R(s) is reduced to evaluation of a small number of inequalities -\/ a number which is bounded above by twice the number of neighbouring seeds.

The discrete nature of the S\+K\+IZ algorithm makes it well suited to image segmentation. The V\+O\+I\+SE algorithm \mbox{[}2\mbox{]} relies on a fast and dynamic method of recalculation of Voronoi diagrams upon addition and removal of seeds, so the two are a natural fit. Although a standalone version of the S\+K\+IZ algorithm is included here (mostly for testing), the main functionality is provided by the matlab bindings in push\+VD, grab\+VD, add\+Seed\+To\+VD and remove\+Seed\+From\+VD, which are compiled into Matlab-\/readable M\+EX binaries and are tailored specifically for the code built and maintained by P. Guio and N. Achilleos to aid faster image analysis through V\+O\+I\+SE.\hypertarget{index_install_sec}{}\section{Installation}\label{index_install_sec}
\hypertarget{index_step1}{}\subsection{Step 1\+: Compile}\label{index_step1}
(1) Open a terminal. Navigate to voise-\/1.\+3/matlab/cpp/build.

(2) Execute command\+: cmake ..

(3) Execute command\+: make

Compilation should take a few minutes.\hypertarget{index_references_sec}{}\section{References}\label{index_references_sec}
\mbox{[}1\mbox{]} R. E. Sequeira and F. J. Preteux. Discrete voronoi diagrams and the skiz operator\+: a dynamic algorithm. I\+E\+EE Transactions on Pattern Analysis and Machine Intelligence, 19(10)\+:1165–1170, 1997. \mbox{[}doi\+: 10.\+1109/34.\+625128\mbox{]}

\mbox{[}2\mbox{]} P. Guio and N. Achilleos. The voise algorithm\+: a versatile tool for automatic segmentation of astronomical images. Monthly Notices of the Royal Astronomical Society, 398(3)\+:1254–1262, 2009. \mbox{[}doi\+: 10.\+1111/j.1365-\/2966.\+2009.\+15218.\+x\mbox{]} 